04_DESeq2

### 2020-09-02 analysis/boneyard/boneyard.Rmd
ready for new fig 23

>>>>

```{r}
comparisonlevelscontrol <- c("control_bldg", "control_lay",  "control_inc.d3",  
                          "control_inc.d9",   "control_inc.d17",  
                          "control_hatch", "control_n5", "control_n9")

comparisonlevelsbldg <- c( "bldg_lay",  "bldg_inc.d3",  
                             "bldg_inc.d9", "bldg_inc.d17",  
                             "bldg_hatch", "bldg_n5", "bldg_n9")

comparisonlabelscharnobldg <- c("lay\ninc3", 
                          "inc3\ninc9", "inc.d9\ninc17", 
                          "inc17\nhatch" , "hatch\nn5", "n5\nn9")

comparisonlabelscontrol <- c("bldg\ncontrol" ,"lay\ncontrol", "inc3\ncontrol", 
                                "inc9\ncontrol", "inc17\ncontrol", 
                                "hatch\ncontrol" , "n5\ncontrol", "n9\ncontrol")

comparisonlabelsbldg <- c("lay\nbldg", "inc3\nbldg", 
                                "inc9\nbldg", "inc17\nbldg", 
                                "hatch\nbldg" , "n5\nbldg", "n9\nbldg")

comparisonlevelsremoval <- c("inc.d3_m.inc.d3", "inc.d9_m.inc.d9", 
                             "inc.d17_m.inc.d17", "hatch_m.n2")

comparisonlablelsremoval <- c("m.inc.d3", "m.inc.d9", 
                              "m.inc.d17", "m.n2")

comparisonlevelsreplace <- c("hatch_early", "inc.d17_prolong",  "hatch_prolong", 
                             "extend_hatch", "n5_extend")

comparisonlablelssreplace <- c("hatch\nearly", "inc.d17\nprolong",  "hatch\nprolong", 
                             "extend\nhatch", "n5\nextend")
